---
title: "Software Usage Promotion Campaign Uplift Modeling"
author: "Martin MacFarlane"
date: "Sept 10, 2024"
output: github_document
---

Initial data exploration was done in "Software Usage Promotion Campaign.ipynb" and exported to "multi_attribution_update.csv".

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#import libraries
```{r, message=FALSE}
library(cobalt)
library(WeightIt)
library(lmtest)
library(sandwich)
library(knitr)
library(ggplot2)
library(rmarkdown)
library(dplyr)
library(tidyverse)
```

```{r, message = FALSE}
# Load file as dataframe
df <- read.csv("multi_attribution_update.csv")
```

```{r, message=FALSE}
# inspect dataframe
print(head(df))
```

```{r, message=FALSE}
# Inspect the data
str(df)
summary(df)
```

Defining 3 separate treatment variables: "tech_support", "discount" "tech_discount".  The latter which will combine the effect of both tech_support and discount on the outcome variable "revenue".

```{r, message=FALSE}
# Define treatment and outcome
treatment1 <- df$tech_support
treatment2 <- df$discount
treatment3 <- df$tech_discount
outcome <- df$revenue
```

Creating balance tables for the 3 treatment variables to obtain the standardized mean difference and variance ratio for each treatment.  SMD values should be +/- 0.1 and Variance Ratio values should be between 0.5 - 2.  The treatment and control groups are not well balanced and weighting will be needed.

```{r, message=FALSE}
# Balance table to show SMD and variance ratio between groups

print("Balance Table for Tech Support")
bal.tab(
    x = treatment1 ~ global + major + smc + commercial + it_spend + employee_count,
    data = df,
    binary = "std",
    disp.v.ratio = TRUE   
)

print("Balance Table for Discount")
bal.tab(
    x = treatment2 ~ global + major + smc + commercial + it_spend + employee_count,
    data = df,
    binary = "std",
    disp.v.ratio = TRUE,
)

print("Balance Table for Tech Support and Discount")
bal.tab(
    x = treatment3 ~ global + major + smc + commercial + it_spend + employee_count,
    data = df,
    binary = "std",
    disp.v.ratio = TRUE,
)
```

Perform the inverse probability of treatment weighting (IPTW) procedure for each treatment to see if we can minimize imbalance between the treatment groups before estimating the causal treatment effect.

```{r, message=FALSE}
# create propensity scores with WeightIt
weight1 <- weightit(treatment1 ~ global + major + smc + commercial + it_spend + employee_count, data = df, method = "ps", estimand = "ate")

weight2 <- weightit(treatment2 ~ global + major + smc + commercial + it_spend + employee_count, data = df, method = "ps", estimand = "ate")

weight3 <- weightit(treatment3 ~ global + major + smc + commercial + it_spend + employee_count, data = df, method = "ps", estimand = "ate")
```

```{r, message=FALSE}
# check the summary
summary(weight1)
summary(weight2)
summary(weight3)
```

The weighted summary statisics seem reasonable as does the adjusted size of the control and treated groups.  We'll now re-check the SMC and variance ratio of the weighted groups.

```{r, message=FALSE}
# check balance using cobalt
print("Balance Table for Tech Support")
bal.tab(
    weight1,
    data = df,
    binary = "std",
    disp.v.ratio = TRUE)

print("Balance Table for Discount")
bal.tab(
    weight2,
    data = df,
    binary = "std",
    disp.v.ratio = TRUE)

print("Balance Table for Tech Support and Discount")
bal.tab(
    weight3,
    data = df,
    binary = "std",
    disp.v.ratio = TRUE)
```

Visualize the balance of the adjusted vs unadjusted groups

```{r, message=FALSE, fig.width=8, fig.height=8}
# visualize the balance
love.plot(
    weight1,
    binary = "std",
    thresholds = c(m = 0.1),
    title = "Love Plot for Tech Support")

love.plot(
    weight2,
    binary = "std",
    thresholds = c(m = 0.1),
    title = "Love Plot for Discount")

love.plot(
    weight3,
    binary = "std",
    thresholds = c(m = 0.1),
    title = "Love Plot for Tech Support and Discount")
```

The groups appear to be well balanced.

Let's create an alternate set of weighted groups to see if we can improve the balance.  We'll remove employee_count and it_spend from the covariates and add size and pc_count.

```{r, message=FALSE}
# recreate propensity scores with updated covariates (remove employee_count and it_spend -- adding size and pc_count)
weight1a <- weightit(treatment1 ~ global + major + smc + commercial + pc_count + size, data = df, method = "ps", estimand = "ate")

weight2a <- weightit(treatment2 ~ global + major + smc + commercial + pc_count + size, data = df, method = "ps", estimand = "ate")

weight3a <- weightit(treatment3 ~ global + major + smc + commercial + pc_count + size, data = df, method = "ps", estimand = "ate")
```

Creating balance tables for our new weighted groups.  The values all seem to fall within acceptable ranges.

```{r, message=FALSE}
# check balance using cobalt
print("New Balance Table for Tech Support")
bal.tab(
    weight1a,
    data = df,
    binary = "std",
    disp.v.ratio = TRUE)

print("New Balance Table for Discount")
bal.tab(
    weight2a,
    data = df,
    binary = "std",
    disp.v.ratio = TRUE)

print("New Balance Table for Tech Support and Discount")
bal.tab(
    weight3a,
    data = df,
    binary = "std",
    disp.v.ratio = TRUE)
```

Visualize the balance of the adjusted vs unadjusted groups for the alternative weights.

```{r, message=FALSE}
# visualize the balance
love.plot(
    weight1a,
    binary = "std",
    thresholds = c(m = 0.1),
    title = "New Love Plot for Tech Support")

love.plot(
    weight2a,
    binary = "std",
    thresholds = c(m = 0.1),
    title = "New Love Plot for Discount")

love.plot(
    weight3a,
    binary = "std",
    thresholds = c(m = 0.1),
    title = "New Love Plot for Tech Support and Discount")
```

Creating balance plots for our original weights.

```{r, message=FALSE}
# Balance plot of propensity scores before and after weighting
bal.plot(
    weight1,
    var.name = "prop.score",
    which = "both"
)

bal.plot(
    weight2,
    var.name = "prop.score",
    which = "both"
)

bal.plot(
    weight3,
    var.name = "prop.score",
    which = "both"
)

```

Creating balance plots for our new weights.

```{r, message=FALSE}
# Balance plot of propensity scores before and after weighting of updated weights
bal.plot(
    weight1a,
    var.name = "prop.score",
    which = "both"
)

bal.plot(
    weight2a,
    var.name = "prop.score",
    which = "both"
)

bal.plot(
    weight3a,
    var.name = "prop.score",
    which = "both"
)
```

Both groups appear to be well balanced.  We will continue with a weighted generalized regression model using our new weights which allows for non-normal distributions.

```{r, message=FALSE}
# weighted regression for treatment 1
model1a <- glm(outcome ~ treatment1 + global + major + smc + commercial + pc_count + size, data = df, weights = weight1a$weights)
summary(model1a)

# robust standard errors
coeftest(model1a, vcov = vcovHC(model1a, type = "HC3"))
```

```{r, message=FALSE}
# weighted regression for treatment 2
model2a <- glm(outcome ~ treatment2 + global + major + smc + commercial + pc_count + size, data = df, weights = weight2a$weights)
summary(model2a)

# robust standard errors
coeftest(model2a, vcov = vcovHC(model2a, type = "HC3"))
```

```{r, message=FALSE}
# weighted regression for treatment 3
model3a <- glm(outcome ~ treatment3 + global + major + smc + commercial + pc_count + size, data = df, weights = weight3a$weights)
summary(model3a)

# robust standard errors
coeftest(model3a, vcov = vcovHC(model3a, type = "HC3"))
```

## Interpretation

### Treatment 1 - Tech Support
Our model predicts that when tech support is provided, an increase in revenue of approximately $7,143 is expected with a standard error of about $208.

While holding all other variables constant, companies that have global offices create addition revenue of approximately $3,801.  Similarly, companies that are large consumers in their industry (major) and companies that are classified as "commercial" create additional revenue of approximately $1,485 and $1,252 respectively.

The number of computers a company has can also be used to predict additional revenue.  Every computer a company has can potentially generate an additional $47 in revenue. 

### Treatment 2 - Discount
Our model predicts that when a discount is provided, an increase in revenue of approximately $5,692 is expected with a standard error of about $250.

While holding all other variables constant, companies that have global offices create addition revenue of approximately $4,328.  Similarly, companies that are large consumers in their industry (major) and companies that are classified as "commercial" create additional revenue of approximately $2,547 and $585 respectively.

The number of computers a company has can also be used to predict additional revenue.  Every computer a company has can potentially generate an additional $49 in revenue. 

### Treatment 3 - Tech Support and Discount
Our model predicts that when tech support AND a discount is provided, an increase in revenue of approximately $8,485 is expected with a standard error of about $230.

While holding all other variables constant, companies that have global offices create addition revenue of approximately $4,108.  Similarly, companies that are large consumers in their industry (major) and companies that are classified as "commercial" create additional revenue of approximately $2,135 and $851 respectively.

The number of computers a company has can also be used to predict additional revenue.  Every computer a company has can potentially generate an additional $47 in revenue. 

While all 3 treatments are likely to created additional revenue, combining both tech support and a discount will likely create more.  However, the benefit of providing a discount on top of tech support is only around $1,342 and so the costs of providing tech support and a discount should be taken into account to ensure that revenue is being maximized.

The company's profile should also be taken into account as companies with global offices, who are large consumers in their industry, who are classified as "commercial" and have a large number of computers will also affect their revenue in a positive way.

## Further Considerations

The costs of providing tech support and the amount of discount provided are not known.  These costs should be further investigated to ensure that revenue is being maximized.  
